---
title: "Prediction Human Activity Recognition"
output: html_document
---
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset). 


# 1. Loading Data

```{r}
trainRaw<- read.csv("./data/pml-training.csv",sep="," , na.strings=c("NA","","#DIV/0!"))
dim(trainRaw)
str(trainRaw)

testRaw<- read.csv("./data/pml-testing.csv",sep="," , na.strings=c("NA","","#DIV/0!"))
dim(testRaw)
```

# 2. Cleaning Data
There are so many NA values is shown.
I'll count na value by each columm, then remove columns which contains NA value and no need to predict like name, timestamp etc.
```{r}
naCntByCol <- apply(trainRaw, 2, function(x) { sum(is.na(x)) })
trainData <- trainRaw[,which(naCntByCol == 0)]
trainData <- trainData[,8:60]
dim(trainData)
testData <- testRaw[,which(naCntByCol == 0)]
testData <- testData[,8:60]
dim(testData)
```

# 3. Fit a Model
## 3.1 Partitioning Data
```{r}
library(caret)
set.seed(123455)
inTrain <- createDataPartition(y = trainData$classe,p=0.7,list=F)
training <- trainData[inTrain,]
testing <- trainData[-inTrain,]
```

## 3.2 Fit a model
Build a Random Forest model
```{r, cache=TRUE}
modFit <- train(classe ~ . , data=training, method="rf", prox=TRUE, preProcess=c('knnImpute', 'center', 'scale')
                        ,trControl = trainControl(method = "cv", number = 5, allowParallel = TRUE) )
modFit
```

## 3.3 Calculate Accuracy on training data
```{r, cache=TRUE}
trainPred <- predict(modFit, training)
confusionMatrix(data = trainPred, reference = training$classe)
```

## 3.4 Calculate out of sample error on the training-test data set
```{r}
testPred <- predict(modFit, testing)
confusionMatrix(data = testPred, reference = testing$classe)
```
Accuracy is 0.0995 / 99.5%. It's not bad. :)


# 4. Prediction on test data set ( pml-testing.csv )
```{r}
prediction <- predict(modFit, testData)
prediction
```

#5. Creating 20 test cases file for "Prediction Assignment Submission"
```{r}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(prediction)
```